{基于 ICEEMDAN 多特征分解和Prophet-}{GRU-NN组合模型多步预测短期风速}

### 2022-04-23 paper.tex
Latest push
Signed-off-by: Hollow Man <hollowman@opensuse.org>

选用真实发电场所的气象数据验证模型。结果表明，使用本文提出的多特征
ICEEMDAN-Prophet-GRU-NN模型，提前12小时预测短期风速的精度会明显提升，因而具有优越性。
}{短期风速预测，组合模型，神经网络，深度学习，数据科学}

@@

We use meteorological data from the actual power station to verify the model.
The results show that by using the multi-feature ICEEMDAN-Prophet-GRU-NN
model proposed in this paper, we can significantly improve the accuracy of
short-term wind speed prediction 12 hours in advance, so it has supremacy.
}}
{short-term wind speed forecast; 
hybrid model; neural network; deep learning; data science.
}

%生成目录
\tableofcontents
% \thispagestyle{empty}

\begingroup
\renewcommand{\addvspace}[1]{}
\newcommand{\loflabel}{图} 
\renewcommand{\numberline}[1]{\loflabel~#1\hspace*{1em}}
\listoffigures

\newcommand{\lotlabel}{表}
\renewcommand{\numberline}[1]{\lotlabel~#1\hspace*{1em}}
\listoftables
\endgroup

@@

\rightline{2022年5月于兰州大学榆中校区萃英山下}
\end{document}

>>>>

选用真实发电场所的气象数据验证模型。结果表明，使用本文提出的多特征
ICEEMDAN-Prophet-GRU-NN模型，提前12小时预测短期风速的精度会明显提升，因而具有优越性。
}{短期风速预测；组合模型；神经网络；深度学习；数据科学}

@@

We use meteorological data from the actual power station to verify the model.
The results show that by using the multi-feature ICEEMDAN-Prophet-GRU-NN
model proposed in this paper, we can significantly improve the accuracy of
short-term wind speed prediction 12 hours in advance, so it has supremacy.
}}
{short-term wind speed forecast, 
hybrid model, neural network, deep learning, data science
}

%生成目录
\addtocontents{toc}{\protect\thispagestyle{empty}}
\tableofcontents

\begingroup
\pagenumbering{gobble}
\renewcommand{\addvspace}[1]{}
\newcommand{\loflabel}{图} 
\renewcommand{\numberline}[1]{\loflabel~#1\hspace*{1em}}
\listoffigures

\newcommand{\lotlabel}{表}
\renewcommand{\numberline}[1]{\lotlabel~#1\hspace*{1em}}
\listoftables
\clearpage
\endgroup

@@

\rightline{2022年5月于兰州大学榆中校区萃英山下}

\end{document}
